\begin{enumerate}[label=\arabic*.]
    \item \textbf{$x \in E_x$} \\
        Let $f$ be the characteristic function of the problem.
        \begin{gather*}
            f(x) = \begin{cases}
                1 \ \ \ \ \text{if } x \in E_x \\
                0 \ \ \ \ \text{if } x \notin E_x
            \end{cases}
        \end{gather*}
        Suppose $f$ is computable. Now define $g$ by:
        \begin{gather*}
            g(x) = \begin{cases}
                x \ \ \ \ \ \text{if } x \notin E_x \text{ or } f(x) = 0 \\
                \uparrow \ \ \ \ \ \text{if } x \in E_x \text{ or } f(x) = 1
            \end{cases}
        \end{gather*}
        $g(x)$ is computable by Church's thesis. Therefore there exists $e$ such that $g(x) \cong \phi_e$. Now we have:
        \begin{gather*}
            \phi_e(x) \downarrow \iff x \in W_x \iff x \in E_x \\
            \phi_e(x) \downarrow \iff x \in W_x \iff x \notin E_x
        \end{gather*}
        This gives us the contradiction. Which shows that the assumption of $f$ being a computable function was wrong and $x \in E_x$ is not decidable.
    \item \textbf{$W_x = W_y$} \\
        Let $f(x) \equiv 0$. Since $f$ is computable then there exists $e$ such that $f \cong \phi_e$. Since $f$ is total, then $W_e = \NN$. Now suppose $W_x = W_y$ is decidable. Then the function $g$ is computable. 
        \begin{gather*}
            g(x, y) = \begin{cases}
                1 \ \ \ \ \text{if } W_x = W_y \\
                0 \ \ \ \ O.W.
            \end{cases}
        \end{gather*}
        Now let $g(e, y) = g_e(y)$ for fixed $e$. Since $g$ is computable then $g_e$ is also computable.
        \begin{gather*}
            g_e(y) = 1 \iff W_y = \NN \iff \phi_y \text{ is total} \\
            g_e(y) = 0 \iff W_y \ne \NN \iff \phi_y \text{ is not total}
        \end{gather*} 
        This means that "$\phi_x$ is total" is decidable iff $g_e$ is computable. And since we know that "$\phi_x$ is total" is not decidable, then $g_e$ is not computable which is a contradiction. Therefore $W_x = W_y$ is not decidable. 
    
    \item \textbf{$\phi_x(x) = 0$} \\
        Suppose it is decidable. Let $g$:
        \begin{gather*}
            g(x) = \begin{cases}
                1 \ \ \ \ \ \text{if } \phi_x(x) = 0 \\
                0 \ \ \ \ \ \text{if } \phi_x(x) \ne 0
            \end{cases}
        \end{gather*}
        Since $\phi_x(x) = 0$ is decidable, then $g$ is computable. Thus there exists $e$ such that $g(x) \cong \phi_e(x)$. Now we have:
        \begin{gather*}
            \phi_e(e) = 0 \iff g(e) = 0 \iff \phi_e(e) \ne 0
        \end{gather*}
        Which gives us the contradiction, Therefore $\phi_x(x) = 0$ is undecidable.
    
    \item \textbf{$\phi_x(y) = 0$} \\
        If $\phi_x(y) = 0$ is decidable then with $y = x$ we have $\phi_x(x) = 0$ is decidable, which by last part we know is undecidable. Therefore $\phi_x(y) = 0$ is undecidable.
    
    \item \textbf{$x \in E_y$} \\
        If it is decidable, by substituting $y$ with $x$ we have that $x \in E_x$ is decidable, which by part 1 we know is undecidable, Therefore $x \in E_y$ is undecidable.
    
    \item {$\phi_x$ is total and constant}
        \begin{gather*}
            f(x, y) = \begin{cases}
                1 \ \ \ \ \ \text{if } x \in W_x \\
                \uparrow  \ \ \ \ \text{if } x \notin W_x
            \end{cases}
        \end{gather*}
        By Church's thesis $f$ is computable, therefore by \smn\ theorem there exists total computable function $k$ such that $f(x, y) = \phi_{k(x)}(y)$.
        \begin{gather*}
            x \in W_x \implies f(x, y) \equiv 1 \implies \phi_{k(x)} \text{ is total and constant} \\
            x \notin W_x \implies f(x, y) \uparrow \implies \phi_{k(x)} \text{ is not total and constant}
        \end{gather*}
        Thus $\phi_{k(x)}$ is total and constant if and only if $x \in W_x$. Since $x \in W_x$ is undecidable, then "$\phi_{k(x)}$ is total and constant" is undecidable, which means "$\phi_x$ is total and constant" is undecidable.
    
    \item $W_x = \emptyset$
        \begin{gather*}
            f(x, y) = \begin{cases}
                x \ \ \ \ \ \text{if } x \in W_x \\
                \uparrow \ \ \ \ \text{if } x \notin W_x
            \end{cases}
        \end{gather*}
        By Church's thesis $f$ is computable, therefore by \smn\ theorem there exists a total computable function $k$ such that $f(x, y) \cong \phi_{k(x)}(y)$.
        \begin{gather*}
            x \in W_x \implies f(x, y) \equiv 1 \implies \phi_{k(x)}(y) \equiv 1 \implies W_{k(x)} = \NN \\
            x \notin W_x \implies \forall y (f(x, y) \uparrow) \implies \forall y (\phi_{k(x)}(y) \uparrow) \implies W_{k(x)} = \emptyset
        \end{gather*}
        Thus we have $W_{k(x)} = \emptyset$ iff $x \notin W_x$. Since $x \notin W_x$ is decidable, then $W_{k(x)} = \emptyset$ is undecidable, which means $W_x = \emptyset$ is undecidable.
    
    \item $E_x$ is an infinite set
        \begin{gather*}
            f(x, y) = \begin{cases}
                y \ \ \ \ x \in W_x \\
                \uparrow \ \ \ x \notin W_x
            \end{cases}
        \end{gather*}
        By Church's thesis $f$ is computable, therefore by \smn\ theorem there exists a total computable function $k$ such that $f(x, y) \cong \phi_{k(x)}(y)$. 
        \begin{gather*}
            x \in W_x \implies \forall y (f(x, y) = y) \implies W_{k(x)} = \NN \\
            x \notin W_x \implies \forall y(f(x, y) \uparrow) \implies W_{k(x)} = \emptyset
        \end{gather*}
        This means that the set $W_{k(x)}$ is infinite iff $x \in W_x$. And since $x \in W_x$ is undecidable, then "$W_{k(x)}$ is an infinite set" is undecidable, which means "$W_x$ is an infinite set" is undecidable.

    \item $\phi_x = g$
        \begin{gather*}
            f(x, y) = \begin{cases}
                g(y) \ \ x \in W_x \\
                \uparrow \ \ \ \ \ x \notin W_x
            \end{cases}
        \end{gather*}
        By Church's thesis $f$ is computable, therefore by \smn\ theorem there exists a total computable function $k$ such that $f(x, y) = \phi_{k(x)}(y)$.
        \begin{gather*}
            x \in W_x \implies f(x, y) = g(y) \implies \phi_{k(x)} = g \\
            x \notin W_x \implies f(x, y) \ne g(y) \implies \phi_{k(x)} \ne g
        \end{gather*}
        Therefore $\phi_{k(x)} = g$ iff $x \in W_x$, since $x \in W_x$ is undecidable, then "$\phi_{k(x)} = g$ is undecidable, which means $\phi_x = g$ is undecidable.
\end{enumerate}