
\begin{enumerate}[label=\ilabel]
    \item 
        Suppose $g_1 \in g.\stab(x).\inv g$.
        \begin{gather*}
            \exists g_2 \in \stab(x): g_1 = g g_2 \inv g \\
            g_1 gx = g g_2 \inv g (gx) = g g_2x = gx \implies g_1 \in \stab(gx)\\
            \implies g.\stab(x).\inv g \subset \stab(gx)
        \end{gather*}
        Now suppose $g_1 \in \stab(gx)$.
        \begin{gather*}
            g_1 gx = gx \implies \inv g (g_1gx) = \inv g (gx) \\
            \implies \inv g g_1 gx = x \implies \inv g g_1 g \in \stab(x) \\
            \implies g(\inv g g_1 g) \inv g = g_1 \in g.\stab(x).\inv g \\
            \implies \stab(gx) \in g.\stab(x).\inv g
        \end{gather*}
        Therefore $\stab(gx) = g.\stab(x).\inv g$.
        Let two members of orbit of $x$ be $g_1x$ and $g_2x$. We know that conjugation is surjective since:
        \begin{gather*}
            x, y \in G: gx\inv g = g y \inv g \implies x = y
        \end{gather*}
        This shows that if $H$ is a subset of $G$ then $|gH\inv g| = |H|$.
        \begin{gather*}
            |\stab(g_1x)| = |g_1.\stab(x).\inv g_1| = |\stab(x)| = |g_2.\stab(x).\inv g_2| = |\stab(g_2x)|
        \end{gather*}
        Thus $|\stab(g_1x)| = |\stab(g_2x)|$.
    \item      
        We saw in class that: $|O_{x_0}| = |G/G_{x_0}|$. Where $O_{x_0}$ is orbit of $x_0$ and $G_{x_0}$ is stabilizer of $x_0$.
        Now consider the set of equations where $g \in G, x \in X: gx = x$, denoted by $N(G \to X)$.
        \begin{gather*}
            N(G \to X) = \underset{g \in G}{\cup} \text{fix}(g)
        \end{gather*}
        And since fix($g_1$) and fix($g_2$) represent different equations therefore:
        \begin{gather*}
            |N(G \to X)| = \underset{g \in G }{\sum}\text{fix}(g)
        \end{gather*}
        And also we have:
        \begin{gather*}
            N(G \to X) = \underset{x \in X    }{\cup} G_x
        \end{gather*}
        And since $G_{x_1}$ and $G_{x_2}$ represent different equations therefore:
        \begin{gather*}
            |N(G \to X)| = \underset{x \in X   }{\sum } |G_x|
        \end{gather*} 
        By part (\textit{i}) we know that elements in the same orbit have stabilizers with the same size therefore:
        \begin{gather*}
            |N(G \to X)| = \underset{x \in I }{\sum } |G_x|.|O_x| = \underset{x \in I }{\sum }|G_x|.|G|/|G_x| = \underset{x \in I }{\sum }|G| = N |G|
        \end{gather*}
        Where $I$ is a set with exactly one element from each orbit and $N$ number of orbits.
        Therefore:
        \begin{gather*}
            \underset{x \in G }{\sum}\text{fix}(g) = N |G|
        \end{gather*}
    \item 
        Assuming $|X| > 1$. Since it is transitive there is only one orbit thus:
        \begin{gather*}
            |G|= \underset{g \in G }{\sum} \text{fix}(g)
        \end{gather*}
        Since $1 \in G$ fixes everything in $X$, if every element in $G$ fixes at least one memeber then we would have:
        \begin{gather*}
            \underset{g \in G }{\sum} \text{fix}(g) = |G| - 1 + \text{fix}(1) > |G|
        \end{gather*}
        Therefore there exists $g \in G$ where fix($g$) = 0.
\end{enumerate}